### 2017-05-15 Publications/Original Software Publications/Science of Computer Programming/reply letter/letter.tex
updating reply letter
Signed-off-by: Felipe R. Monteiro <rms.felipe@gmail.com>

    \begin{quote}
    \textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: which reference would you suggest to use here? Add a reference to some book on GPU. You can also briefly explain the term and then cite the reference.}}
    \end{quote}

>>>>

    \begin{quote}
    \textcolor{blue}{\textbf{Response:} We have replaced this term by ``CUDA (parallel) streams and events'' and indicated ``Professional CUDA C Programming'' book as reference.}
    \end{quote}
